Staged Abstract Interpreter

### 2018-01-29 paper/paper.tex
update

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  We present Staged Abstract Interpreter
\end{abstract}

@@

\cite{Boucher:1996:ACN:647473.727587}'s work is esentially a partial evaluated
CE abstract interpreter written in a big-step semantics for CPS. The analysis
it can perform is monovariant. We reproduce their abstractly complied analysis
by adding explicit staging annotation to CE abstract interpreter.
Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.

\subsection{CPS Syntax and Concrete Interpreter}

@@

@@

@@

Generalize the idea to staged CESK abstract machine for direct style (or ANF), 
which has fully power for instantiating different analyses.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  It is well known that a staged interpreter is a compiler. A nature question is to ask that what would be for a staged abstract interpreter and how to do that.
\end{abstract}

@@

\citeauthor{Boucher:1996:ACN:647473.727587} introduced abstract compilation as a new
implementation technique for abstract interpretation based static analysis \cite{Boucher:1996:ACN:647473.727587}.
Their work is esentially a partial evaluated CE (\textit{Control-Environment}) abstract
interpreter written in a big-step semantics for programs written in continuation-passing style.
The analysis it can perform is a monovariant control flow analysis, sepcifically, Shiver's original
formulation of 0-CFA \cite{Shivers:1991:SSC:115865.115884, Shivers:1988:CFA:53990.54007}.
After the partial evaluation on input program, the \textit{control} part of abstract interpreter
is disappeared, instead, the compiled analysis is a closure (higher-order function) and
only takes an environment as argument,
and the overhead of traversing the abstract syntax tree of source program also has been eliminated.
Since the target language is written a continuation-passing style, so there is
no explict evaluation context component when constructing the abstract interpreter
(rather than a CEK machine).

In this section, we firstly review their work of closure generation, and reproduce abstractly complied analysis
by adding explicit staging annotation to the CE abstract interpreter.
Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.

\subsection{Syntax and Concrete Semantics}
Continuation-passing style (CPS) is a widely used intermediate representation in compilation and analysis for functional
languages.

@@

\subsection{Closure Generation}

@@

(Fianally, we should briefly summarize the difference between them: staging vs partial evaluation; code generation; engineering effort; performance)

@@

Generalize the idea to staged CESK abstract machine for direct style (or ANF), 
which has fully power for instantiating different analyses. We need to show that
it not merely reproduces abstract compilation by staged computation.
